Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-08-22 Multiresolution_framework/ltx/response_to_reviews.tex

Best Regards,
\\

Parham Aram.

\section{Handling editor}
\begin{enumerate}
\item Whilst the paper does fit the scope of NI, I agree with R1 and R3, that explicit advantages of going to a multi-resolution frame - in addition to the conceptual ones - compared to the prior work based on Gaussian basis functions needs clarification and elucidation.

\emph{The first paragraph of the newly added ``8.1 State-Space Representation'' subsection in the Discussion  highlights the benefits of the MRAIDE compared to the prior work. We also added a paragraph to ``Estimation algorithm'' in the Discussion to clarify the benefits of the novel M-step presented in this work compared to the implementation in Dewar et al. (2009). Please refer to Responses 1 and 5 to R1 for more details.}

@@

\item  In addition, at least a ``proof of principle" inversion from empirical data would enhance the potential impact of the paper.

\emph{We agree that the use of empirical data will strengthen the paper. Unfortunately, we do not have access to the appropriate data at present. However, we understand that several other groups are now collecting high resolution data that is appropriate for the methods developed in this paper. We believe that the methods developed in this paper are equally important as the development of high  resolution spatiotemporal recording techniques and together, these approaches have enormous potential to answer some of the biggest questions in neuroscience. The ability to use mathematical models as filters, or lenses into the brain, is still a relatively new concept to many members of our community. This new lens allows us to image aspects of neurophysiology of individual subjects that are normally hidden in electrical recordings. Therefore, we believe it is important to continue to improve our methods that will lead to the next era in systems neuroscience, where mathematical modeling, experimental measures and model-data fusion will become standard methods. Furthermore, we believe that (good) experimental design is based upon the availability of analysis tools. Therefore, new imaging tools, like the framework presented in this paper, will lead to new data being collected and potential advances in our collective knowledge of brain function.}

@@

		% \emph{\parham{Section 5 summarizes important characteristics of B-Spline scaling and wavelet functions which are collected from different references, with an attempt to clarify the inner product and convolution of theses functions (please see R2 comment on ``B-spline calculus''). We think that this brief review can familiarize interested readers  with  B-spline scaling and wavelet functions and direct them to the important literature on this matter. As the reviewer suggested the calculation of the Fourier transform is now moved to the appendix.}}

\emph{As the reviewer suggested, moving the calculation of the Fourier transform to the Appendix will provide a better flow to the paper. This has been done.}

\emph{We understand that this section will not be the central focus of the paper for some members of our research community, however we believe that it is important that this information remains in the paper to allow for implementation without the requirement of digesting information from several texts.}

\emph{We have had similar feedback to your suggestion from our colleagues prior to submission of the paper. Interestingly, the feedback from the people with expertise in wavelet theory thought that the overview of the estimation methods was essential, but the section on wavelets should be reduced. Conversely, people with expertise in the estimation methods thought the overview on wavelets was critical and the section on EM-algorithm should be reduced. We completely appreciate R1's comments and suggestions, but since R2 commented on the usefulness of this section we would very much like to leave it in. We believe that different sections will be valuable for people with different specializations, the synthesis of this information is a valuable contribution for implementation for a wide audience.}

@@

\emph{In order to formulate the state-space representation of the multi-resolution neural field model, the inner product of the B-spline functions are required. We believe that it is necessary to provide the interested reader with the required tools to implement the algorithm. Appendix D of Freestone et al. (2011) and Appendix A herein are only similar in the sense that the inner product of two basis functions are calculated. In Appendix D of Freestone et al. (2011), two  n-dimensional Gaussians are considered, while here the inner product of two B-spline functions is calculated. We have no objections to removing Appendix C. However, as stated above, we think that it would be informative for the broad audience of NeuroImage to include the model-specific derivations and some of the well-known formulations of the EM algorithm, since it draws on a wide range of literature.}

        \item Although I value the use of a wavelet as opposed to a Gaussian basis, the advantages in the context of the analysis of brain imaging data have not been demonstrated and a comparison with the authors' earlier approach has not been performed.

\emph{To respond to this important comment we have added ``8.1 State-Space Representation'' subsection into the discussion.}

		\item{The framework of Freestone et al. (2011), seemed not to assume a linear relation between mean membrane potential and firing rate and in that sense the present approach appears more restrictive.}

@@

        \item The authors say that a multi-resolution approach would explain the``organizational level of the brain at which cognition and behaviour are best explained'' but it is unclear what the alternative levels considered here are and what the significance of the results obtained is.

\emph{Within our framework, the alternate levels are defined by the spatial scales of the wavelet decomposition. The significant result is the formulation of a model when various spatial scales of a neural field can be simultaneously represented. The ability to image the multi-dimensional neural field will lead to a better understanding of the important spatial scales when neural information processing occurs.}

		\item Similar claims to the ones mentioned here regarding implications for ``patient-specific'' modeling have also been made in Freestone et al. (2011), so it is not clear how these relate to the current multi-resolution approach and also such remarks might look too ambitious given that only synthetic data with fixed parameters are considered.

	\emph{Please refer to Response 2 to the handling editor. \dean{In summary, the framework can be used to create patient-specific models when it is applied with patient-specific data. Demonstrating convergence with synthetic data, where actual states and parameters are known, is a necessary first step. Furthermore, there is a significant body of work where various phenomena have been replicated using the neural field equations. This motivates the creation of tools to verify the models and experimentally test hypotheses that computational studies have generated.    }}

@@

	\item The comments about model complexity and parsimony on p.13 are somehow vague as these quantities are undefined.

				% \emph{\parham{some notes to be added to the manuscript: Parsimony: as few as necessary variables to describe a phenomenon, complexity: to add detail description to the model to increase its accuracy with the natural phenomenon, finding a balance between complexity and parsimony is crucial. By parsimony we sacrifice realism ...  }}

		\emph{To clarify this comment, a short paragraph has been included in Section 6 to better explain the modeling choices facing every user. That is, choosing between a more parsimonious or more complex model structure.  For the audience with less experience in system identification, a reference with further information regarding this topic has also been included.}

@@

		\item The comments on large scale networks and delays made on p.20 look irrelevant to the present framework.

		\emph{We have omitted the last paragraph of the discussion on delays in large scale networks.}

@@

		\item Much of the discussion of the last section focuses on technical issues, while the discussion of the observation kernel chosen on p.17 is limited.

		\emph{We have added a paragraph in the new subsection ``8.1 State-Space Representation'' in the Discussion, regarding the choice of the observation kernel.}

### 2012-08-22 Multiresolution_framework/ltx/response_to_reviews.tex

Best Regards,
\\

Parham Aram.

\section{Handling editor}
\begin{enumerate}
\item Whilst the paper does fit the scope of NI, I agree with R1 and R3, that explicit advantages of going to a multi-resolution frame - in addition to the conceptual ones - compared to the prior work based on Gaussian basis functions needs clarification and elucidation.

\emph{The first paragraph of the newly added ``8.1 State-Space Representation'' subsection in the Discussion  highlights the benefits of the MRAIDE compared to the prior work. We also added a paragraph to ``8.2 Estimation Algorithm'' in the Discussion to clarify the benefits of the novel M-step presented in this work compared to the implementation in Dewar et al. (2009). Please refer to Responses 1 and 5 to R1 for more details.}

@@

\begin{enumerate}
    \item As a minor comment, I would suggest changing the notation for the scaling and wavelet coefficients in Eq. (6), for example into normal lowercase `a' and `c', respectively. The $\beta$ might be confused by B-spline notation.

	\emph{We have changed the scaling and wavelet coefficients into normal lowercase `a' and `c', respectively.}

\item For the discussion, it might be useful to add a sentence that the basis structure (i.e., non-redundant, versus a (tight) frame representation) is a requirement for this framework.

\emph{We have added a sentence to Sect. 8.1 (now 8.2) for the basis structure requirement.}

@@

\emph{We have added this comment to Sect. 8.2 (now 8.3).}

 % 
 % \begin{figure*}[!ht]
 % \begin{center}
 % \includegraphics{./Graph/pdf/fig1.pdf} 
 % \end{center}
 % \caption{}
 % \label{fig:Figure1}
 % \end{figure*}

\end{enumerate}

    \section{Reviewer 3}  
    \subsection{Main Concerns}
		\begin{enumerate} 
			\item I am not at all sure that isotopic scaling of the multi-resolution is appropriate for brain connections, but I cannot say at this point that it is not.

			\emph{It is generally accepted that the intracortical connectivity structure is isotropic. However, as the reviewer pointed out, this is not the case for cortico-cortical connectivity. \dean{Nevertheless, the presented framework is also valid for other connectivity kernels provided they are spatially homogeneous and that they can be approximated by a set of weighted isotropic basis functions (that can form a net anisotropic kernel).} The connectivity kernel can take any arbitrary shapes but this may require more basis functions for an accurate reconstruction.}

@@

			\item This model cries out for validation in real neuronal systems, but alas, at this point we only see convergence to synthetic data.

			 \emph{\dean{We agree with this statement 100 percent. We hope that this paper will motivate new experiments, where neural field models can be experimentally validated. It has now been nearly 40 years since neural field models where introduced in computational studies. For the first time we are at the exciting point in time where computing power and estimation algorithms are sufficiently advanced to link models to actual data. This is why we believe the framework the is introduced in this paper has the potential to make an impact.} For further remarks regarding this point please refer to Response 2 to the handling editor.}
		 % 			
		 % \emph{\parham{The authors appreciate that the only way to truly validate the proposed framework is with real data. However, before validating the method on real data, we believe that it is essential to first validate the estimation method using accepted models and synthetic data, where the true and estimated parameters can be compared. We believe this was achieved in this paper. The title of the manuscript was chosen to reflect this fact, stating this is a multi-resolution framework for the Amari type neural field model. In an effort to make the method employed in the paper more explicit, we have added ``data was generated synthetically using Amari neural field model'' to the Results section.}}

@@

		\item This audience needs to have all symbols, including commonly used ones such as `equality over distribution', double font domains like R and Z, and jargon terms such as `lead field'.

		\emph{We have defined independent and identically distributed (i.i.d.) random variables under Eq. (5). The double font domains are added to Table 1. A brief description of `lead field' is also added below Eq. (5).}

	\dean{I am up to here!!!~~~~~~~XXXXXX~~~~~~}		
		\item Frankly, I would off-load all of the very difficult mathematics to the appendices and supplementary data, and focus a NeuroImage paper on the results of image analysis.

@@

			\emph{Response here.}

			% \item Contrasting, for example, this multiresolution method with Freestone's 2011 results would be helpful for continuity.
			% 
			% \emph{Response here.}

@@

\dean{Cant we just upload it?}

			\end{enumerate}  
			\subsection{Moderate Concerns} 
			\begin{enumerate} 
			 \item Page 2: the authors should clearly define the difference between neural field and neural mass models.

			\emph{\parham{We have added the following paragraph on page 2: The main difference between these two classes is that neural field models describe the spatiotemporal evolution of a particular variable such as firing rate, membrane voltage, or synaptic activity defined as the statistical expectation taken over a neural population, while neural mass models describe such a quantity over time only, assuming that neurons are localized at approximately the same spatial location.}}

			\item Eq. 3: theta needs indexing

			\emph{We have rewritten Eq. 2 by removing the parameter $\theta$ in order to be consistent with the rest of equations in the manuscript, and we have described the coupling strength or synaptic efficiency within the text under Eq. 2.}

@@

			\item Define first and second order synaptic responses (used in Figure 2 to explain text that does not refer to these terms)

			\emph{Definitions of first and second-order synaptic responses have been added to the text under Eq 2.}

@@

			\item{Eq. 9: the state variables $x$ seem to arise without distinction from $v$}

			\emph{The units of $x$ are also Volts. However, the states are weights for particular levels of resolution, where $v$ is the total net field. We have added a sentence to add clarification in Section \dean{xx}}.

@@

			\item Between Eq. 19 and 20 change
			`write the neural field and connectivity kernel decomposition' To `write the connectivity kernel and neural field decomposition'
			To maintain order with Eqs. 20 and 21.

			\emph{We have changed the text to `the connectivity kernel and neural field decomposition' to maintain consistency with Eqs. 20 and 21.}
